Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2017-02-19 article_review/reviewer_letter.tex
minor changes in rewiever letter

{\color{blue} The new academic application is in dimension $10$. For higher-dimensional "real-life" examples, our procedure should still work well given that the effective dimension of a model is often way smaller than its nominal dimension. Furthermore, the estimator ``Correlation 2'' is really efficient at revealing inputs with small main effects.}
\end{itemize}

@@

First, the cost of constructing the error threshold is a computational cost and not a numerical cost. That is, it does not require extra model evaluations. This specificity is further discussed in the answer to point 2.

Secondly, we claim that the precision of our procedure should be better than those based on confidence intervals (asymptotic or bootstrap based) obtained with random sampling methods. In our approach, the construction of the error bounds makes use of the analytical expression of the Sobol' indices. At the opposite, errors bounds in confidence intervals are estimated entirely from the sampling points and are less accurate.

To back up this claim, the precision of our procedure is compared to bootstrap confidence intervals obtained from random sampling. The comparison is carried out for the wing weight example. Results show that for an equivalent number of evaluations, the precision of bootstrap confidence intervals is far less accurate than the precision of our procedure.}

>>>>

{\color{blue} The new academic application is in dimension $10$. For higher-dimensional "real-life" examples, our procedure should still work well given that the effective dimension of a model is often way smaller than its nominal dimension. Furthermore, the estimator ``Correlation 2'' is really efficient at identifying inputs with small main effects.}
\end{itemize}

@@

First, the cost of constructing the error threshold is a computational cost and not a numerical cost. That is, it does not require extra model evaluations. This specificity is further discussed in the answer to comment 2. below.

Secondly, we claim that the precision of our procedure should be better than those of random sampling methods using confidence intervals (asymptotic or bootstrap based). In our approach, the construction of the error bounds makes use of the analytical expression of the Sobol' indices. At the opposite, errors bounds in confidence intervals are estimated entirely from the sampling points and are less accurate.

To back up this claim, the precision of our procedure is compared to bootstrap confidence intervals obtained from random sampling. The comparison is carried out for the bratley test function in Section 5.3. Results show that for an equivalent number of evaluations, random methods using confidence intervals are less accurate than our procedure.}
